|

### 2025-07-09 output/IMPS-2025-slideshow.qmd
Add item color palette to the preface

@@

ITEMS_PALETTE <- c(
  PALETTE_BLUE["normal"],
  PALETTE_RASPBERRY["normal"],
  PALETTE_APPLE["normal"]
) |>
  unname() |>
  setNames("prob" |> paste(1:3, sep = '_'))

@@

logit <- function(x) 1 / (1 + exp(-x))
irf   <- function(a, b, theta) logit(a * (theta - b))

@@

logit_curve_data_long <- logit_curve_data |>
  pivot_longer(starts_with("prob"), names_to = "item", values_to = "prob")

>>>>

# Item colors:
ITEMS_PALETTE <- c(
  PALETTE_BLUE["normal"],
  PALETTE_RASPBERRY["normal"],
  PALETTE_APPLE["normal"],
  PALETTE_TANGERINE["normal"],
  PALETTE_UNED["medium"]
) |>
  unname() |>
  setNames(1:5)

@@

@@

@@

logit_curve_data_long <- logit_curve_data |>
  pivot_longer(starts_with("prob"), names_to = "item", values_to = "prob") |>
  mutate(item = item |> str_remove("prob_"))
